---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dverse

<!-- badges: start -->
[![R-CMD-check](https://github.com/maurolepore/dverse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maurolepore/dverse/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/maurolepore/dverse/graph/badge.svg)](https://app.codecov.io/gh/maurolepore/dverse)
<!-- badges: end -->

The goal of dverse is to document a universe. It creates a data frame containing
the metadata associated with the documentation of a collection of R packages. It
allows for linking topic names to their corresponding documentation online.

If you maintain a meta-package, dverse helps create a comprehensive reference
for its website.

## Installation

Install from CRAN:

``` r
install.packages("dverse")
```

or get a development version from GitHub:

``` r
# install.packages("pak")
pak::pak("maurolepore/dverse")
```

## Motivation

The [Tidyverse](https://www.tidyverse.org/) popularized the idea of a "universe
of packages." The typical universe has a meta-package that centralizes access to
functions and data across all its packages. For example, with `library(tidyverse)` the [tidyverse
meta-package](https://tidyverse.tidyverse.org/) centralizes access to the
functions in [glue](https://glue.tidyverse.org/),
[tibble](https://tibble.tidyverse.org/), and several other packages in the
[Tidyverse universe](https://www.tidyverse.org/).

However, meta-packages typically don't centralize documentation. For example,
the tidyverse website only shows the [documentation the tidyverse meta-package
itself](https://tidyverse.tidyverse.org/reference/index.html) and does not show
the [documentation for glue](https://glue.tidyverse.org/reference/index.html),
[tibble](https://tibble.tidyverse.org/reference/index.html), and other packages
in the Tidyverse.

The [dverse](https://maurolepore.github.io/dverse/) package solves this problem.
It creates a data frame containing the metadata associated with the
documentation of any set of packages. This data frame can be easily used to
generate the universe-wide reference for the meta-package website, for example
using [pkgdown](https://pkgdown.r-lib.org/).

## Example

```{r main}
library(dverse)
library(glue)
library(tibble)

universe <- c("glue", "tibble")

# Example URLs:
# https://glue.tidyverse.org/reference/as_glue.html
# https://tibble.tidyverse.org/reference/as_tibble.html

url_template <- "https://{package}.tidyverse.org/reference/{topic}.html"

docs <- document_universe(universe, url_template)
docs
```

Typically you would hide the code (`echo = FALSE`) and generate click-able links
with `DT::datatable()` or `knitr::kable()`. For example, this code to generates
the table under "All functions in my universe":

```{r kable, eval=FALSE}
# Picking only a few rows and columns for a short example
pick <- docs[c("topic", "title", "package")]
knitr::kable(head(pick, 3))
```

### All functions in my universe

This is a basic, universe-wide reference generated with dverse.

```{r echo=FALSE, ref.label="kable"}

```

For customization ideas see `?DT::datatable()`, `?knitr::kable()`, and the
examples in the [dverse
articles](https://maurolepore.github.io/dverse/articles).
