---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dverse

<!-- badges: start -->
[![R-CMD-check](https://github.com/maurolepore/dverse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maurolepore/dverse/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/maurolepore/dverse/graph/badge.svg)](https://app.codecov.io/gh/maurolepore/dverse)
<!-- badges: end -->

The goal of dverse is to document a universe. It creates a data frame containing
the metadata associated with the documentation of a collection of R packages. It
allows for linking topic names to their corresponding documentation online. If
you maintain a universe meta-package, it helps create a comprehensive reference
for its website.

## Installation

Install from CRAN:

``` r
install.packages("dverse")
```

or get a development version from GitHub:

``` r
# install.packages("pak")
pak::pak("maurolepore/dverse")
```

## Example

```{r}
# Use dverse and the universe of packages you want to document
library(dverse)
library(tools)
library(datasets)

universe <- c("datasets", "tools")
url_template <- "https://www.rdocumentation.org/packages/{package}/versions/3.6.2/topics/{topic}.html"

document_universe(universe, url_template = url_template)
```
