---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

on_ci <- isTRUE(as.logical(Sys.getenv("CI", "false")))
```

# dverse

<!-- badges: start -->
[![R-CMD-check](https://github.com/maurolepore/dverse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maurolepore/dverse/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/maurolepore/dverse/graph/badge.svg)](https://app.codecov.io/gh/maurolepore/dverse)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/dverse)](https://CRAN.R-project.org/package=dverse)
<!-- badges: end -->

The goal of dverse is to document a universe. It creates a data frame containing
the metadata associated with the documentation of a collection of R packages. It
allows for linking topic names to their corresponding documentation online.

If you have a meta-package, dverse helps you to create a comprehensive reference
for its website.

## Installation

Install from CRAN:

``` r
install.packages("dverse")
```

or get a development version from GitHub:

``` r
# install.packages("pak")
pak::pak("maurolepore/dverse")
```

## Motivation

The [Tidyverse](https://www.tidyverse.org/) popularized the idea of a "universe
of packages." The typical universe has a meta-package that centralizes access to
functions and data across all its packages. For example, with `library(tidyverse)` the [tidyverse
meta-package](https://tidyverse.tidyverse.org/) centralizes access to the
functions in [dplyr](https://dplyr.tidyverse.org/),
[ggplot2](https://ggplot2.tidyverse.org/), and several other packages in the
[Tidyverse universe](https://www.tidyverse.org/).

However, meta-packages typically don't centralize documentation. For example,
the tidyverse website only shows the [documentation for the tidyverse meta-package
itself](https://tidyverse.tidyverse.org/reference/index.html) but does not show
the [documentation for dplyr](https://dplyr.tidyverse.org/reference/index.html),
[ggplot2](https://ggplot2.tidyverse.org/reference/index.html), and other packages
in the Tidyverse.

The [dverse](https://maurolepore.github.io/dverse/) package solves this problem.
It creates a data frame containing the metadata associated with the
documentation of any set of packages. This data frame can be easily used to
generate the universe-wide reference for the meta-package website, for example
using [pkgdown](https://pkgdown.r-lib.org/).

## Example

* `document_universe()` creates a data frame with documentation metadata of one or
more packages.
* `url_template` can take different templates for the manual and vignettes.
* `knitr::kable()` turns the URLs into clickable links. `DT::datatabe()` also
provides a search box.

```{r}
library(dverse)
# Universe
library(glue)
library(tibble)

packages <- c("glue", "tibble")
template <- "https://{package}.tidyverse.org/reference/{topic}.html"
docs <- document_universe(packages, template)

docs
```

```{r}
#| eval: !r on_ci
#| echo: !r on_ci
DT::datatable(docs)
```

```{r}
#| eval: !r on_ci
#| echo: !r on_ci
knitr::kable(tail(docs))
```

