---
title: "Get started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Basics

`dverse::document_universe()` creates a data frame with the documentation of a
collection of R packages. `url_template` links each `topic` in each `package`
with its corresponding documentation online.

```{r}
library(glue)
library(tibble)

packages <- c("glue", "tibble")
url_template <- "https://{package}.tidyverse.org/reference/{topic}.html"
docs <- dverse::document_universe(packages, url_template)

docs
```

You may generate a clickable table is with `knitr::kable()`.

```{r}
knitr::kable(head(docs, 3))
```

You may generate a clickable and searchable table with `DT::datatable()`.

```{r}
DT::datatable(docs, escape = FALSE)
```

## Tweaks

* See `?knitr::kable()` for more options.

```{r}
knitr::kable(head(docs, 3), format = "html", col.names = NULL, escape = FALSE)
```

* See `?DT::datatable()` for more options.

```{r}
options <- list(dom = "fti", search = list(search = "glue"))
DT::datatable(docs, escape = FALSE, rownames = NULL, options = options)
```
