---
title: "Get started"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`dverse::document_universe()` creates a data frame with the documentation of a
collection of R packages. `url_template` links each `topic` in each `package`
with its corresponding documentation online.

```{r}
library(dplyr, warn.conflicts = FALSE)
# Universe
library(glue)
library(tibble)

packages <- c("glue", "tibble")
url_template <- "https://{package}.tidyverse.org/reference/{topic}.html"
docs <- dverse::document_universe(packages, url_template)

docs
```

Pick rows and columns to organize the documentation however you like (e.g. by
`package` or `type`).

```{r}
pick <- docs %>% 
  filter(type == "help", keyword != "internal" | is.na(keyword)) %>% 
  select(topic, title, package)
pick
```

You may generate a clickable table with `DT::datatable()`, which offers great
options and features such as a search box.

```{r}
options <- list(dom = "fti", search = list(search = "glue"))
DT::datatable(pick, escape = FALSE, rownames = NULL, options = options)
```

See `?DT::datatable()` for more options.
