---
title: "Get started"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

`dverse::document_universe()` creates a data frame with the documentation of a
collection of R packages. `url_template` links each `topic` in each `package`
with its corresponding documentation online.

```{r}
library(dverse)
# Universe
library(glue)
library(tibble)
# Other
library(dplyr)
library(DT)

packages <- c("glue", "tibble")
url_template <- "https://{package}.tidyverse.org/reference/{topic}.html"
docs <- dverse::document_universe(packages, url_template)
docs
```

You may need to exclude reexported objects from other packages, which links are
broken.

```{r}
online <- docs %>% filter(dverse::is_online(topic))
```

Documentation is of multiple kinds.

```{r}
online %>% count(type, keyword)
```

You may organize it however you like.

```{r}
vignettes <- online %>% filter(type == "vignette")
everything_else <- online %>% anti_join(vignettes)
```

#### Vignettes

```{r}
vignettes %>%
  select(topic, title, package) %>%
  datatable(escape = FALSE)
```

#### Everything else

```{r}
everything_else %>%
  select(topic, title, package) %>%
  # Showing off some options from `DT::datatable()`
  datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(dom = "fti", search = list(search = "glue"))
  )
```
