---
title: "Get started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Basics

* `dverse::document_universe()` creates a data frame with the documentation of a
collection of R packages. Provide a `url_template` to link each `topic` in each
`package` with its corresponding documentation online.

```{r}
library(glue)
library(tibble)

packages <- c("glue", "tibble")
url_template <- "https://{package}.tidyverse.org/reference/{topic}.html"
docs <- dverse::document_universe(packages, url_template)

docs
```

You may generate a clickable table is with `knitr::kable()`.

```{r}
knitr::kable(docs)
```

You may generate a clickable and searchable table with `DT::datatable()`.

```{r}
DT::datatable(docs, escape = FALSE)
```

## Tweaks

* See `?knitr::kable()` and `?kableExtra::column_spec()` for more options.

```{r}
knitr::kable(
  docs, 
  format = "html",
  col.names = NULL,
  escape = FALSE
) %>%
kableExtra::column_spec(1, bold = TRUE) %>% 
kableExtra::column_spec(2, width = "20em")
```

* See `?DT::datatable()` for more options.

```{r}
DT::datatable(
  docs,
  escape = FALSE,
  rownames = NULL,
  options = list(
    # fti =  f: filter, t: table, i: information
    dom = "fti", search = list(search = search)
  )
)
```
