---
title: Get started
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to create a global search for any collection of R
packages, i.e. a universe. Your universe may be on CRAN, large, and popular like
the [tidyverse](https://tidyverse.org/). But it may also be not on CRAN, small,
company-specific or personal.

The example here uses the 'toyverse' -- a toy universe containing the packages
glue and dplyr.

You need:

* the package dverse to <u>d</u>ocument your uni<u>verse</u>, 
* each package in the 'toyverse' to access the documentation metadata,
* DT to create a searchable table.

```{r packages}
library(dverse)

# toyverse
library(glue)
library(dplyr)

library(DT)
```

`dverse::document_universe()` takes the names of the packages in the
'toyverse', and a template pointing to each help file (topic) in each
package.

```{r docs}
toyverse <- c("glue", "dplyr")
# For example: https://dplyr.tidyverse.org/reference/select.html
template <- "https://{package}.tidyverse.org/reference/{topic}.html"

docs <- dverse::document_universe(toyverse, template)
docs
```

You may need to exclude some topics, such as reexported objects from other
packages. Because topics outside your universe yield broken links, you can
exclude them with `dverse::is_online()`.

```{r online}
docs %>% filter(!dverse::is_online(topic))

online <- docs %>% filter(dverse::is_online(topic))
```

Consider the different kinds of documentation in your universe.

```{r kinds}
online %>% count(type, keyword)
```

You may organize the documentation however you like. For inspiration see the
[pactaverse](https://rmi-pacta.github.io/pactaverse/articles/global-search.html),
the toy
['admiralverse'](https://maurolepore.github.io/admiralverse/articles/reference.html),
[fgeo](https://forestgeo.github.io/fgeo/articles/siteonly/reference.html) and
[tidymodels](https://www.tidymodels.org/find/).

Here it makes sense to place vignettes, datasets, and public functions
in separate tables.

### Vignettes

Here are all the vignettes available across packages in the 'toyverse'.
Click on each topic to read its corresponding vignette.

```{r vignettes}
vignettes <- online %>% filter(type == "vignette")

vignettes %>%
  distinct(topic, title, package) %>%
  datatable(escape = FALSE)
```

#### You don't see what you expect?

* This works with vignettes but not articles, so `usethis::use_vignette()` not
`usethis::use_article()`.

* When you install the packages in your universe ensure to install the vignettes.
Vignettes install by default when you install your packages from CRAN with
`install.packages()` or `pak::pak()`. But if you install them from source with
`devtools::install()` or `remotes::install_github()`, then you need `build_vignettes
= TRUE`.

### Datasets

Here are all the datasets. Click on each topic to read about it.

```{r datasets}
datasets <- online %>% filter(keyword == "datasets")

datasets %>%
  distinct(topic, title, package) %>%
  datatable(escape = FALSE)
```

### Functions

Here are all the functions, except internal ones. Click on each topic to read about it.

```{r public}
internal <- online %>% filter(keyword == "internal")

public <- online %>%
  anti_join(vignettes) %>%
  anti_join(datasets) %>%
  anti_join(internal)

public %>%
  distinct(topic, title, package) %>%
  datatable(escape = FALSE)
```

### Learn More

To learn more see the toy 'admiralverse'
[meta-package](https://maurolepore.github.io/admiralverse) -- which models the
main use case of dverse.

You may also enjoy these videos:

* Creating a meta-package for the toy 'admiralverse' ([5'](https://youtu.be/ezVpsadSF7A)).
* Creating a website for the toy 'admiralverse' ([9'](https://youtu.be/VhmnADBDXv0)).
