---
title: "Get started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Basics

```{r}
library(dplyr, warn.conflicts = FALSE)
# Use dverse and the universe of packages you want to document
library(dverse)
library(glue)
library(tibble)

universe <- c("glue", "tibble")
url_template <- "https://{package}.tidyverse.org/reference/{topic}.html"
documentation <- document_universe(universe, url_template = url_template)

# Note that {topic} and {pacakge} refer to column names
documentation
```

You may generate a clickable table is with `knitr::kable()`.

```{r}
pick <- select(documentation, topic, title, concept, package)

# Removing column names for cleaner output
knitr::kable(head(pick), col.names = NULL)
```

You may generate a searchable table with `DT::datatable()`.

```{r}
# `escape = FALSE` shows the link (defaults to showing the underlying URL)
DT::datatable(pick, escape = FALSE)
```

### Organization and customization

In a meta-package you may organize the documentation of the entire universe in a
single place, maybe organized by package or concept (via `#'
@family`). You may create your own custom tables with `DT` or other packages.

```{r}
custom_table <- function(data, search = "") {
  DT::datatable(
    data,
    escape = FALSE,
    rownames = NULL,
    options = list(
      # fti =  f: filter, t: table, i: information
      dom = "fti", search = list(search = search)
    )
  )
}
```

* By package

```{r}
custom_table(filter(pick, package == "glue"), search = "safe")
```

* By concept

```{r}
custom_table(filter(pick, concept == first(concept)))
```

### Presentation

In a meta-package, you may use dverse in an article, then use it to [override
the default Reference
component](https://pkgdown.r-lib.org/articles/customise.html#navbar-heading).

For an example see the pkgdown Reference of
[dverse](https://maurolepore.github.io/dverse/) and follow the link to its
source and see how it's configured in
[_pkgdown.yml](https://github.com/maurolepore/dverse/blob/main/_pkgdown.yml).

